---
title: "PSY 8960 Final Project - Part 4"
author: "Saron Demeke"
date: "`r Sys.Date()`"
output: 
  html_document:
    df_print: paged
knit: (function(input, ...) { 
        rmarkdown::render(input, output_file='../markdown/final_dashboard.html') })
---
  
# Script Settings and Resources
```{r section1, message=F}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
```  
  

# Data Import and Cleaning
```{r section2}
full_dat <- read_rds("../rds/combined_dataset.rds")

skinny_dat <- full_dat %>% 
  select(EmployeeID, MonthlyIncome, Attrition, JobSatisfaction,
         Department, EducationField, Gender, JobRole) %>% 
  mutate(Attrition_num = ifelse(Attrition == "Yes", 1, 0), .after = Attrition) %>% 
  saveRDS("../shiny/people_dashboard/final_shiny_dat.RDS")
```


To view the shiny app created for this final project, [click here](http://rmarkdown.rstudio.com/authoring_shiny.html).



In console 
> library(rsconnect)
> rsconnect::setAccountInfo(name='sdemeke', token='74B7FDE39775CF5443EF9C632829F3DA', secret='0gmweLocppD0paHwx8WbIDkX40YHsvLbu3UraWaI')
> getwd()
[1] "C:/Users/demek004/Documents/SP23_PSY8960_DataScience/psy8960-final/R"
> deployApp("../shiny/people_dashboard")


Using selectInput and checkBoxInput
checkBoxInput allows multiple selections


Output
When shiny passes input to the output functions, column names are passed as character vectors. We can apply data masking procedure from
'args_data_masking {rlang}' help file using '.data[[var]]' to pass the input variable as a live data-variable that is readable within the pipe.




